PANCHANGE_data_preprocessing

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Cleaned up/added some comments in the script

*** MD - need to adapt for participants with missing data (should be NA)
```{r gad sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_prepan <- c(1,1,1,1,1,1,1)

@@

Calculate sum score for PCL-6
```{r pcl sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_prepan <- c(1,1,1,1,1,1)

@@

*** MD - need to adapt for participants with missing data (should be NA)
```{r phq sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
phq.items_key_prepan <- c(1,1,1,1,1,1,1,1,1)

@@

*** MD - need to adapt for participants with missing data (should be NA)
```{r ocir sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
ocir.items_key_prepan <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

@@

>>>>

*Note that scores with missingness will be changed to NA later in the script
```{r gad sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_prepan <- c(1,1,1,1,1,1,1)

@@

Calculate sum score for PCL-6

*Note that scores with missingness will be changed to NA later in the script
```{r pcl sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_prepan <- c(1,1,1,1,1,1)

@@

*Note that scores with missingness will be changed to NA later in the script
```{r phq sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
phq.items_key_prepan <- c(1,1,1,1,1,1,1,1,1)

@@

*Note that scores with missingness will be changed to NA later in the script
```{r ocir sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
ocir.items_key_prepan <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

@@

*Note that the COPING GLAD OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
